IMSIL currently supports 1-D, 2-D, and rotational symmetric 3-D geometries forstatic simulations, and 1-D geometries for dynamic simulations.\textbf{1-D geometries} describe layered targets with surfaces and interfacesparallel to the $x$-$y$ plane. They are therfore defined by an array of $z$coordinates which correspond to the position of the top surface, anyinterfaces between layers (regions), and the bottom surface. Semi-infinite andinfinite targets may be approximated by large enough values of the surfacecoordinates. 1-D geometries combined with \textbf{cylindrical or spherical symmetry} describetargets composed of cylindrical or spherical shells. The surface and interfacepositions then refer to the distance from the symmetry line or center. The``top'' surface is the inner surface, and the ``bottom'' surface the outersurface. If a hollow body is not desired, the position of the inner surface hasto be assigned a negative value.During a \textbf{dynamic simulation}, the cell densities are allowed to changeuntil some threshold is reached for the deviation from equilibrium. Then thecell geometries are adapted so that the densities relax towards equilibrium.\textbf{2-D geometries} are defined by polygons in the $x$-$z$ plane. Thepolygons are defined by vertices and their connectivity (for details seeSection~\ref{s:geom}). Since these specifications can be lengthy, they can beput into a separate geometry file. 2-D geometries also may be specified to beperiodic in $x$ direction. Internally, the geometry information is convertedinto a distance array for each region. The distance values are defined on a meshcovering the respective region.\textbf{3-D rotational symmetric geometries} may be realized by combining 2-Dgeometries with cylindrical symmetry. For a symmetry axis parallel to the $x$axis, the 3-D geometry is defined by rotating the polygons about this axis.Other orientations of the symmetry axis are realized by permutations of $x$,$y$, and $z$ \cite{bradley_second_2021}.Finally, a simple \textbf{surface roughness} model is provided for both 1-D and2-D simulations. This so-called density gradient model\cite{lindsey_simple_2017} reduces the target density linearly towards thesurface in a sub-surface layer. The model has been introduced to provide morerealistic sputter yields at glancing incidence. \begin{center}\begin{tabular}{lll}parameter \quad                   & IMSIL name    & to be specified in record \\\hlinenumber of regions                 & \texttt{NR}      & \texttt{\&SETUP} \\dimensionality                    & \texttt{NDIM}    & \texttt{\&SETUP} \\1-D surface/interface coordinates & \texttt{POSIF}   & \texttt{\&GEOM} \\cylindrical symmetry flag         & \texttt{LCYLX}   & \texttt{\&GEOM} \\                                  & \texttt{LCYLY}   & \texttt{\&GEOM} \\                                  & \texttt{LCYLZ}   & \texttt{\&GEOM} \\spherical symmetry flag           & \texttt{LSPHER}  & \texttt{\&GEOM} \\position of symmetry line/center  & \texttt{CENTER}  & \texttt{\&GEOM} \\number of ions for cell update    & \texttt{NIONUPD} & \texttt{\&GEOM} \\threshold change for cell update  & \texttt{FRACUPD} & \texttt{\&GEOM} \\fixed coordinate in cell update   & \texttt{POSFIX}  & \texttt{\&GEOM} \\2-D geometry file                 & \texttt{GEOMFILE} & \texttt{\&GEOM} \\polygon vertices                  & \texttt{POS}     & \texttt{\&GEOM} \\polygon connectivity              & \texttt{POINTS}  & \texttt{\&GEOM} \\periodicity flag                  & \texttt{LPERX}   & \texttt{\&GEOM} \\periodic boundary positions       & \texttt{XPER}    & \texttt{\&GEOM} \\box width of distance grid        & \texttt{WBOX2}   & \texttt{\&GEOM} \\maximum size of distance grid     & \texttt{NBOX2}   & \texttt{\&GEOM} \\thickness of roughness layer      & \texttt{WROUGH}  & \texttt{\&GEOM} \\\end{tabular}\end{center}