For \textbf{static simulations}, the target is composed of \textbf{regions}.Each region is described by a material and a geometry. The \textbf{material} isprimarily defined by its name, which is a chemical formula similar to the ionname. The \textbf{density} of a region is set to the weighted densities of theelementary materials by default, or can be specified by the user. Note that forcompound targets, the weighted densities are often inaccurate, so theirdensities should be specified in the input file. Another material property is its \textbf{crystallinity}. If the material iscrystalline, the crystal structure is defined in the \texttt{CRYSTAL} record. Inaddition, the crystallographic directions of the surface normal and of a surfacevector may be specified. Alternatively, the material may be specified aspolycrystalline, in which case a new random orientation of the crystal is chosenfor each ion. A further material property is the RMS \textbf{thermal vibration} amplitude ofthe atoms, which may either be calculated from the Debye theory using the targetand Debye temperature, or it may be specified directly. Thermal vibrations areonly relevant in crystalline targets.For \textbf{dynamic simulations}, the \texttt{\&MATERIAL} record can be used tospecify the initial material name and density. These specifications areconverted into atom densities, which are used to initialize the cell contents.The cell densities are then allowed to change during the simulation. Since theother material properties depend on the target composition, they can only be interpolated from the elemental material properties. Crystalline targets are notallowed in dynamic simulations. \begin{center}\begin{tabular}{lll}parameter \quad                 & IMSIL name    & to be specified in record \\\hlinenumber of regions               & \texttt{NR}        & \texttt{\&SETUP} \\material name                   & \texttt{NAME}      & \texttt{\&MATERIAL} \\elementary material density     & \texttt{DENSITY}   & \texttt{\&ATOMS} \\material density                & \texttt{DENSITY}   & \texttt{\&MATERIAL} \\crystallinity flag              & \texttt{XTAL}      & \texttt{\&MATERIAL} \\polycrystallinity flag          & \texttt{LPOLY}     & \texttt{\&MATERIAL} \\surface normal                  & \texttt{WAFER}     & \texttt{\&MATERIAL} \\surface vector                  & \texttt{VSURF}     & \texttt{\&MATERIAL} \\target temperature              & \texttt{TEMP}      & \texttt{\&SETUP} \\Debye temperature               & \texttt{TDEBYE}    & \texttt{\&MATERIAL} \\RMS thermal vibration amplitude & \texttt{VIB}       & \texttt{\&MATERIAL} \\\end{tabular}\end{center}