IMSIL currently supports 1-D, 2-D, and 3-D geometries forstatic simulations, and 1-D geometries for dynamic simulations. Static simulations may also use rotational symmetry to simplify geometry defnitionand/or accelerate simulation. \textbf{1-D geometries} describe layered targets with surfaces and interfacesparallel to the $x$-$y$ plane. They are therefore defined by an array of $z$coordinates which correspond to the position of the top surface, anyinterfaces between layers (regions), and the bottom surface. Semi-infinite andinfinite targets may be approximated by large enough values of the surfacecoordinates. 1-D geometries combined with \textbf{cylindrical or spherical symmetry} describetargets composed of cylindrical or spherical shells. The surface and interfacepositions then refer to the distance from the symmetry line or center. The``top'' surface is the inner surface, and the ``bottom'' surface the outersurface. If a hollow body is not desired, the position of the inner surface hasto be assigned a negative value.During a \textbf{dynamic simulation}, the cell densities are allowed to changeuntil some threshold is reached for the deviation from equilibrium. Then thecell geometries are adapted so that the densities relax towards equilibrium. Forfurther details see Section~\ref{s:updates}.\textbf{2-D geometries} are defined by polygons in the $x$-$z$ plane. Thepolygons are defined by vertices and their connectivity (for details seeSection~\ref{s:geom}). Since these specifications can be lengthy, they can beput into a separate geometry file. 2-D geometries also may be specified to beperiodic in $x$ direction. Internally, the geometry information is convertedinto a signed distance function array for each region. The distance values are defined on a regular mesh covering the respective region.\textbf{3-D rotational symmetric geometries} may be realized by combining 2-Dgeometries with cylindrical symmetry. For a symmetry axis parallel to the $x$axis, the 3-D geometry is defined by rotating the polygons about this axis.Other orientations of the symmetry axis are realized by permutations of $x$,$y$, and $z$ \cite{bradley_second_2021}.2-D and arbitrary 3-D geometries may also be defined by signed distance function(SDF) values on a regular grid, provided as external input on files. An SDF specifies the distance of the grid points from the nearest point on theboundary of the region under consideration. It is given a negative signwhen the grid point is outside the region. An SDF must also be provided for the whole simulations domain (= the union of all regions) including a rimof thickness at least equal to the maximum free flight path. (?) All regionSDFs must provide values on the whole simulation domain. Currently, the user is responsible for the consistency of the SDFs.Finally, a simple \textbf{surface roughness} model is provided for both 1-D and2-D simulations. This so-called density gradient model\cite{lindsey_simple_2017} reduces the target density linearly towards thesurface in a sub-surface layer. The model has been introduced to provide morerealistic sputter yields at glancing incidence. \begin{center}\begin{tabular}{lll}parameter \quad                   & IMSIL name    & to be specified in record \\\hlinenumber of regions                 & \texttt{NR}      & \texttt{\&SETUP} \\dimensionality                    & \texttt{NDIM}    & \texttt{\&SETUP} \\1-D surface/interface coordinates & \texttt{POSIF}   & \texttt{\&GEOMETRY} \\cylindrical symmetry flag         & \texttt{LCYLX}   & \texttt{\&GEOMETRY} \\                                  & \texttt{LCYLY}   & \texttt{\&GEOMETRY} \\                                  & \texttt{LCYLZ}   & \texttt{\&GEOMETRY} \\spherical symmetry flag           & \texttt{LSPHER}  & \texttt{\&GEOMETRY} \\position of symmetry line/center  & \texttt{CENTER}  & \texttt{\&GEOMETRY} \\2-D geometry file                 & \texttt{GEOMFILE} & \texttt{\&GEOMETRY} \\polygon vertices                  & \texttt{POS}     & \texttt{\&GEOMETRY} \\polygon connectivity              & \texttt{POINTS}  & \texttt{\&GEOMETRY} \\periodicity flag                  & \texttt{LPERX}   & \texttt{\&GEOMETRY} \\periodic boundary positions       & \texttt{XPER}    & \texttt{\&GEOMETRY} \\box width of distance grid        & \texttt{WBOX2}   & \texttt{\&GEOMETRY} \\maximum size of distance grid     & \texttt{NBOX2}   & \texttt{\&GEOMETRY} \\signed distance function file     & \texttt{SDFFILE} & \texttt{\&GEOMETRY} \\thickness of roughness layer      & \texttt{WROUGH}  & \texttt{\&GEOMETRY} \\\end{tabular}\end{center}