In a \textbf{static} simulation, the target presents itself to all incoming ions as specified in the input file and, optionally, any file read duringsetup (histogram, geometry, or cell file).In a \textbf{dynamic} simulation, the target is updated according to thechanges caused by the simulated collision cascades. IMSIL supports two kinds of dynamic simulation modes:First (``damage accumulation''), the damage to crystalline targets may betaken into account for subsequent trajectories. In this way, the suppression of channeling by damage accumulation may be described. Also, recombination of newly generated defects with damage from previous collision cascades can be taken into account. Second (``dynamic simulation''), it is possible to predict the evolution of the target geometry from the changes in the atom densities of the target.In the version described in this manual, only 1-D targets can be updated in this way.The updates can be done continuously or with a certain frequency. In the sequential version of IMSIL, damage and atom densities are, bydefault, updated as soon as they occur. In the parallel version this would lead to excessive communication between the threads. Therefore, the user has to choose the frequency of these updates in terms of the number of simulated ions between updates. Too frequent updates lead to penalties in execution time, while too infrequent updates may affect the results. In case of geometry updates, it is also possible to specify that updates beperformed only when cell densities have changed more than a threshold. When a geometry update is performed, also the grid for the atom densities isadjusted so that the grid spacings remain approximately the same.\begin{center}\begin{tabular}{lll}parameter \quad                       & IMSIL name & to be specified in record \\\hlinehistogram file                        & \texttt{HISFILE}  & \texttt{\&SETUP} \\geometry file                         & \texttt{GEOMFILE} & \texttt{\&GEOMETRY}\\cell file                             & \texttt{CELLFILE} & \texttt{\&SETUP} \\take damage accumulation into account & \texttt{LDAMDYN}  & \texttt{\&SETUP} \\dynamic simulation mode               & \texttt{LDYN}     & \texttt{\&SETUP} \\number of ions for histogram updates  & \texttt{NIONHIS}  & \texttt{\&SETUP} \\number of ions for geometry updates   & \texttt{NIONGEOM} & \texttt{\&SETUP} \\refined damage model                  & \texttt{LDAM}     & \texttt{\&DAMAGE} \\threshold for geometry update         & \texttt{FRACUPD}  & \texttt{\&GEOMETRY} \\fixed coordinate in 1-D geometry update & \texttt{POSFIX}  & \texttt{\&GEOMETRY} \\\end{tabular}\end{center}